A deeper look into bug fixes: patterns, replacements, deletions, and additions

### 2016-02-17 MSRChallenge2016.tex
update PAR method and result

\subsection{Detecting PAR Bug Fixing Pattern}\label{sec:method}
The bug fixing patterns that we analyze in this work are adopted from Kim et
al. paper~\cite{kim2013}. The following is the description of each considered
pattern. 
\todo{Ferdian: why are we only studying 7?  It's OK to not study all of them,
  but we need to explain why.}
  \begin{enumerate}
	\item {\bf Altering method parameters (AMP)}\\
	{\bf Example:} obj.method(v1,v2) $\rightarrow$ obj.method(v1,v3)\\
	{\bf Description:} This pattern changes the input for method parameters.
	\item {\bf Calling another method with the same parameters (MSM)}\\
	{\bf Example:} obj.method1(param) $\rightarrow$ obj.method2(param)\\
	{\bf Description:} This pattern changes the method name.
	\item {\bf Calling another overloaded method with one more parameter (COM)}\\
	{\bf Example:} obj.method(v1) $\rightarrow$ obj.method(v1,v2)\\
	{\bf Description:} This pattern adds one more parameter to the method.
	\item {\bf Changing a branch condition (CBC)}\\
	{\bf Example:} if(a != b) $\rightarrow$ if(a != b \&\& c == 0)\\
	{\bf Description:} This pattern adds or removes condition.
	\item {\bf Initializing an object (IAO)}\\
	{\bf Example:} Type obj $\rightarrow$ Type obj = new Type()\\
	{\bf Description:} This pattern adds a initialization to object declaration.
	\item {\bf Adding a null checker (ANC)}\\
	{\bf Example:} obj.m1() $\rightarrow$ if(obj!=null){obj.m1()}\\
	{\bf Description:} This pattern inserts a condition to check whether an object is null or not in order to prevent unexpected state.
	\item {\bf Adding an array out of bound checker (AOB)}\\
	{\bf Example:} arr[idx]=0 $\rightarrow$ if(idx<arr.length){arr[idx]=0}\\
	{\bf Description:} This pattern inserts a condition to check that an array index is within bound right before the index is used.
\end{enumerate}

To analyze bug fixing patterns, we utilizes Boa's language
infrastructure~\cite{dyer2013}. It contains a large number of dataset and provide
a domain specific language to perform analysis on source code. Despite this
advantage, Boa still have limited capability that prevents us from performing
precise detection of bug fixing patterns. For example, it is unable to perform a
diff between two file versions, which is needed to compare the pre-fix and the
post-fix version of a buggy file. Thus, rather than finding the exact count of
bug fixing patterns, we will find an approximate count of those patterns. The
following are descriptions on how we detect each pattern.

@@

@@

\subsection{Frequency of PAR Bug Fixing Pattern}\label{sec:freqfixpattern}
After running the bug pattern detection approach on Boa's dataset, I obtained the result shown in Table~\ref{tab:freqpattern}. The result shows that AMC, MSM, COM, CBC, IAO, ANC, and AOB pattern is found on 1.95\%, 1.69\%, 0.58\%, 4.23\%, 2.82\%, 2.90\%, and 0.28\% of buggy files. We can see that the most common pattern among these patterns is CBC and the least common pattern is AOB. If we assume that these patterns never appear together in the dataset, these patterns cover 14.21\% of buggy files. Kim et al. mentioned that the patterns that they use cover almost 30\% of real patches~\cite{kim2013}. Although we only detect 7 out of 10 bug fixing patterns, it is hard to believe that the remaining three patterns cover 15\% of buggy files, especially 14.21\% is a number we get when we assume that the patterns that we detect never appear together. Moreover, the percentage of each pattern is based on imprecise approximation which is likely to represent an upper bound rather than a lower bound. This suggests that common bug fixing patterns might not be as common as it appeared to be.

\begin{table}[!htb]
	\caption{Frequency of Bug Fixing Patterns}\label{tab:freqpattern}
	\centering
	\begin{tabular}{lr} 
		\hline
		& \textbf{GitHub}\\
		\hline
		\#Buggy Files & 46,301,429 \\ 
		\#AMP Pattern & 901,083 \\
		\#MSM Pattern & 783,073 \\
		\#COM Pattern & 270,128 \\ 
		\#CBC Pattern & 1,959,377 \\  
		\#IAO Pattern & 1,308,006 \\  
		\#ANC Pattern & 1,340,561 \\  
		\#AOB Pattern & 128,016 \\  
		\hline
	\end{tabular}
\end{table}

>>>>

\subsection{Detecting PAR Bug Fixing Pattern}\label{sec:method}
The bug fixing patterns that we analyze in this work are adopted from Kim et
al. paper~\cite{kim2013}. The following is the description of each considered
pattern. 
\todo{Ferdian: why are we only studying 7?  It's OK to not study all of them,
  but we need to explain why.}
  \begin{enumerate}
	\item {\bf Altering method parameters (AMP)}\\
	{\bf Example:} obj.method(v1,v2) $\rightarrow$ obj.method(v1,v3)\\
	{\bf Description:} This pattern changes the input for method parameters.
	\item {\bf Calling another method with the same parameters (MSM)}\\
	{\bf Example:} obj.method1(param) $\rightarrow$ obj.method2(param)\\
	{\bf Description:} This pattern changes the method name.
	\item {\bf Calling another overloaded method with one more parameter (COM)}\\
	{\bf Example:} obj.method(v1) $\rightarrow$ obj.method(v1,v2)\\
	{\bf Description:} This pattern adds one more parameter to the method.
	\item {\bf Changing a branch condition (CBC)}\\
	{\bf Example:} if(a != b) $\rightarrow$ if(a != b \&\& c == 0)\\
	{\bf Description:} This pattern adds or removes condition.
	\item {\bf Initializing an object (IAO)}\\
	{\bf Example:} Type obj $\rightarrow$ Type obj = new Type()\\
	{\bf Description:} This pattern adds a initialization to object declaration.
	\item {\bf Adding a null checker (ANC)}\\
	{\bf Example:} obj.m1() $\rightarrow$ if(obj!=null){obj.m1()}\\
	{\bf Description:} This pattern inserts a condition to check whether an object is null or not in order to prevent unexpected state.
	\item {\bf Adding an array out of bound checker (AOB)}\\
	{\bf Example:} arr[idx]=0 $\rightarrow$ if(idx<arr.length){arr[idx]=0}\\
	{\bf Description:} This pattern inserts a condition to check that an array index is within bound right before the index is used.
	\item {\bf Adding a collection out of bound checker (COB)}\\
	{\bf Example:} x=col.get(idx) $\rightarrow$ if(idx<col.size()){x=col.get(idx)}\\
	{\bf Description:} This pattern inserts a condition to check that a collection index is within bound before it is used.
\end{enumerate}

The above patterns only cover 8 out of 10 bug fixing patterns in PAR. The other two patterns are: (1) checking that an object is an instance of a target class before casting it; and (2) replacing expression in an if condition by another expression in the same scope. Pattern (1) cannot be analyzed because Boa does not support {\em instanceof} expression. Similarly, pattern (2) requires us to track scope between pre-fix and post-fix version, which is not supported by Boa. Implementing them ourselves might be possible, but it might require too much effort than necessary. Investigating 8 out of 10 patterns should give us a good idea on how common the patterns actually are.

As mentioned before, we analyze bug fixing patterns by utilizing Boa's language
infrastructure~\cite{dyer2013}. It contains a large number of dataset and provide
a domain specific language to perform analysis on source code. Despite this
advantage, Boa still have limited capability that prevents us from performing
precise detection of bug fixing patterns. For example, it is unable to perform a
diff between two file versions, which is needed to compare the pre-fix and the
post-fix version of a buggy file. Thus, rather than finding the exact count of
bug fixing patterns, we will find an approximate count of those patterns. The
following are descriptions on how we detect each pattern.

@@

\item {\bf COB Pattern}\\
To detect COB pattern, we count the number of if conditional expression that
contains {\em expr<col.size()} or {\em col.size()>expr} for both pre-fix and
post-fix version. If there are count differences between pre-fix and post-fix
version, we consider that COB pattern is found.

@@

\subsection{Frequency of PAR Bug Fixing Pattern}\label{sec:freqfixpattern}
After running the bug pattern detection approach on Boa's dataset, I obtained the result shown in Table~\ref{tab:freqpattern}. The result shows that AMC, MSM, COM, CBC, IAO, ANC, AOB, and COB pattern is found on 1.95\%, 1.69\%, 0.58\%, 4.23\%, 2.82\%, 2.90\%, 0.28\%, and 0.57\% of buggy files. We can see that the most common pattern among these patterns is CBC and the least common pattern is AOB. If we assume that these patterns never appear together in the dataset, these patterns cover 14.78\% of buggy files. Kim et al. mentioned that the patterns that they use cover almost 30\% of real patches~\cite{kim2013}. Although we only detect 8 out of 10 bug fixing patterns, it is hard to believe that the remaining two patterns cover 15\% of buggy files, especially 14.78\% is a number we get when we assume that the patterns that we detect never appear together. Moreover, the percentage of each pattern is based on imprecise approximation which is likely to represent an upper bound rather than a lower bound. This suggests that common bug fixing patterns might not be as common as it appeared to be.

\begin{table}[!htb]
	\caption{Frequency of Bug Fixing Patterns}\label{tab:freqpattern}
	\centering
	\begin{tabular}{lr} 
		\hline
		& \textbf{GitHub}\\
		\hline
		\#Buggy Files & 46,301,429 \\ 
		\#AMP Pattern & 901,083 \\
		\#MSM Pattern & 783,073 \\
		\#COM Pattern & 270,128 \\ 
		\#CBC Pattern & 1,959,377 \\  
		\#IAO Pattern & 1,308,006 \\  
		\#ANC Pattern & 1,340,561 \\  
		\#AOB Pattern & 128,016 \\  
		\#COB Pattern & 262,915 \\   
		\hline
	\end{tabular}
\end{table}
